### 2015-07-08 src/misc/s7_series_list.tex
Created dientry command.

	{ You, us & them: From motor simulation to ascribed shared intentionality in social perception.}

@@

	{Carrots & Sticks - a neurobehavioral investigation of affective outcome processing in psychopathy.}

>>>>

	{ You, us \& them: From motor simulation to ascribed shared intentionality in social perception.}

@@

	{Carrots \& Sticks - a neurobehavioral investigation of affective outcome processing in psychopathy.}
